---
editor_options:
  chunk_output_type: console
---

# NOTES

-   This file is *not* included in the [source package](https://r-pkgs.org/structure.html#sec-source-package) because of the [`.nopurl` suffix in its
    filename](https://pkgpurl.rpkg.dev/reference/purl_rmd.html#-rmd-files-excluded-from-purling).

-   The chunks below have to be manually executed in order to regenerate the package data.

-   Although the datasets below are saved as ["internal data" in `R/sysdata.rda`](https://r-pkgs.org/data.html#sec-data-sysdata), they can still be
    exported and documented (by documenting the dataset's quoted name in the main `.Rmd` source file – which only works when the dataset is also `@export`ed),
    something [not explicitly mentioned](https://coolbutuseless.github.io/2018/12/10/r-packages-internal-and-external-data/) in the book [R
    Packages](https://r-pkgs.org/data.html#sec-data-data). To do so, you first need to manually add the `export()` directive in the NAMESPACE file since
    roxygen2 won't add it automatically.

# Define data

## `metadata_geneva_municipalities_districts`

```{r}
# mapping between two-digit municipality and district codes and their respective names
metadata_geneva_municipalities_districts <-
  readr::read_csv(file = "data-raw/metadata_geneva_municipalities_districts.csv",
                  col_types = "Diicc") %T>%
  assertr::assert_rows(row_reduction_fn = assertr::col_concat,
                       predicate = assertr::is_uniq,
                       municipality_code_2_digits,
                       district_code)
```

## `metadata_geneva_raw_datasets`

The Genevan vote register data is often split among several files per ballot date and oddly named. Thus we compiled additional metadata.

```{r}
# mapping between filenames and ballot dates/types/etc.
metadata_geneva_raw_datasets <- readr::read_csv(file = "data-raw/metadata_geneva_raw_datasets.csv",
                                                col_types = "Dcllllicc")
```

## `pkg_config`

```{r}
pkg_config <-
  tibble::tibble(key = character(),
                 default_value = list(),
                 description = character()) |>
  tibble::add_row(key = "global_max_cache_age",
                  default_value = list("30 days"),
                  description = pkgsnip::md_snip("opt_global_max_cache_age")) |>
  tibble::add_row(key = "path_raw_data",
                  default_value = list(NULL),
                  description = paste0("the path to the directory holding the cantonal raw data files (which are not part of this package due to legal ",
                                       "restrictions and/or concerns regarding voter privacy); see the section *Raw data files* in the package's ",
                                       "[README](https://swissevote.rpkg.dev/#raw-data-files) for further details"))
```

# Write data

Save all the small data objects as a single internal file `R/sysdata.rda`. Note that when documenting them, they must be explicitly `@export`ed to be available
to package users.

```{r}
usethis::use_data(metadata_geneva_municipalities_districts,
                  metadata_geneva_raw_datasets,
                  pkg_config,
                  internal = TRUE,
                  overwrite = TRUE,
                  compress = "xz",
                  version = 3L)
```
