---
output: pal::gitlab_document
---

# `r paste0(pal::desc_value("Package"), ": ", pal::desc_value("Title"))`

`r pal::desc_value("Description")`

## Details

### Raw data files

The **cantonal raw data files** are *not* included in this package due to legal restrictions and/or concerns regarding voter privacy and thus **have to be
provided by the user**. The path to the folder holding these files must be set in the [R option](https://rdrr.io/r/base/options.html)
**`swissevote.path_raw_data`** and the files under this path are expected to be organized and named in the following way:

``` {.fs}
[swissevote.path_raw_data]/
├──BE/
|  ├──BE_YYYY-MM-DD.EXT
|  └──...
├──GE/
|  ├──vYYYYNN.EXT
|  └──...
└──NE/
   ├──NE_YYYY-MM-DD.EXT
   └──...
```

The Genevan raw data files must be named according to the column `filename` in `swissevote:::metadata_geneva_raw_datasets` (which has been defined by the Geneva
State Chancellery). Raw data files from the other cantons must be named by the canton abbreviation and the ballot date (e.g. `NE_2019-02-10`).

### Caching

Time-consuming operations like reading in the raw datasets or scraping ballot dates from cantonal websites are cached to the local filesystem by default (using
[pkgpins](https://gitlab.com/salim_b/r/pkgs/pkgpins)). The maximum cache lifespan for all affected functions can be set in the global option
**`swissevote.global_cache_lifespan`**[^1] (defaults to *30 days* if unset).

[^1]: Its value must be a valid [lubridate duration](https://lubridate.tidyverse.org/reference/as.duration.html#details) which can be a natural-language string
    like `"2 days 1 minute 30 seconds"` (or short `2d1min30s`).

## Installation

```{r, install-snippet-dev, child = pkgsnip::snip_path("installation-notice_dev-version_gitlab.Rmd")}
```

## Development

### Literate Programming

```{r, literate-programming-snippet, child = pkgsnip::snip_path("rmd-package-notice.Rmd")}
```

### Coding Style

```{r, coding-style-snippet, child = pkgsnip::snip_path("coding-style-notice.Rmd")}
```

----------------------------------------------------------------------------------------------------------------------------------------------------------------
