---
output: pal::gitlab_document
---

# `r paste0(pal::desc_value("Package"), ": ", pal::desc_value("Title"))`

`r pal::desc_value("Description")`

## Details

### Raw data files

The **cantonal raw data files** are _not_ included in this package due to legal restrictions and/or concerns regarding voter privacy and thus
**have to be provided by the user**. The path to the folder holding these files must be set in the [R option](https://rdrr.io/r/base/options.html)
**`swissevote.global_cache_lifespan`** and the files under this path are expected to be organized and named in the following way:

```fs
[swissevote.path_raw_data]/
├──BE/
|  ├──BE_YYYY-MM-DD.EXT
|  └──...
├──GE/
|  ├──vYYYYNN.EXT
|  └──...
└──NE/
   ├──NE_YYYY-MM-DD.EXT
   └──...
```

The Genevan raw data files are named according to the column `filename` in `swissevote:::metadata_geneva_raw_datasets` (which has been defined by the Geneva
State Chancellery). Raw data files from the other cantons are named by the canton abbreviation and the ballot date.

## Installation
```{r, install-snippet-dev, child = pkgsnip::snip_path("installation-notice_dev-version_gitlab.Rmd")}
```

## Development

### Literate Programming
```{r, literate-programming-snippet, child = pkgsnip::snip_path("rmd-package-notice.Rmd")}
```

### Coding Style
```{r, coding-style-snippet, child = pkgsnip::snip_path("coding-style-notice.Rmd")}
```

---
