---
output: pal::gitlab_document
---

```{r}
#| label: init
#| include: false

knitr::opts_knit$set(root.dir = getwd())
```

# `r pal::desc_value("Package")`

`r paste0('[![CRAN Status](https://r-pkg.org/badges/version/', pal::desc_value(key = "Package"), ')](https://cran.r-project.org/package=', pal::desc_value(key = "Package"), '){.pkgdown-release}')`

`r pal::desc_value("Description")`

## Details

### Raw data files

The **cantonal raw data files** are *not* included in this package due to legal restrictions and/or concerns regarding voter privacy and thus **have to be
provided by the user**. The path to the folder holding these files must be set via the [package configuration
key](https://pal.rpkg.dev/reference/pkg_config_val.html) **`path_raw_data`** (e.g. by setting the R option `swissevote.path_raw_data`) and the files under this
path are expected to be organized and named in the following way:

``` fs
[swissevote.path_raw_data]/
├──BE/
|  ├──BE_YYYY-MM-DD.EXT
|  └──...
├──GE/
|  ├──vYYYYNN.EXT
|  └──...
└──NE/
   ├──NE_YYYY-MM-DD.EXT
   └──...
```

The Genevan raw data files must be named according to the column `filename` in `swissevote:::metadata_geneva_raw_datasets` (which has been defined by the Geneva
State Chancellery). Raw data files from the other cantons must be named by the canton abbreviation and the ballot date (e.g. `NE_2019-02-10`).

### Caching

Time-consuming operations like reading in the raw datasets or scraping ballot dates from cantonal websites are cached to the local filesystem by default (using
[pkgpins](https://pkgpins.rpkg.dev)). The maximum cache age for all affected functions can be set via the package configuration key **`global_max_cache_age`**
[^1] (defaults to *`r pal::pkg_config_val_default(key = "global_max_cache_age", pkg = "swissevote")`* if unset).

```{r}
#| label: documentation
#| eval: !expr '!isTRUE(getOption("pal.build_readme.is_pkgdown"))'
#| results: asis
#| echo: false
pkgsnip::md_snip(id = "pkgdown_notice") %>%
  paste0("## Documentation\n\n",
         "[![Netlify Status](https://api.netlify.com/api/v1/badges/ce410db6-b85a-4707-9358-f0d3449398c3/deploy-status)]",
         "(https://app.netlify.com/sites/swissevote-rpkg-dev/deploys)\n\n",
         .) %>%
  pal::cat_lines()
```

[^1]: Its value must be a valid [lubridate duration](https://lubridate.tidyverse.org/reference/as.duration.html#details) which can be a natural-language string
    like `"2 days 1 minute 30 seconds"` (or short `2d1min30s`).

## Installation

```{r}
#| label: install-snippet-dev
#| child: !expr pkgsnip::snip_path("installation-notice_dev-version_gitlab.Rmd")
```

```{r}
#| label: usage
#| eval: !expr isTRUE(getOption("pal.build_readme.is_pkgdown"))
#| results: asis
#| echo: false
pkgsnip::md_snip(id = "usage_notice") %>%
  paste0("## Usage\n\n", .) %>%
  pal::cat_lines()
```

## Development

### R Markdown format

```{r}
#| label: rmd-format
#| child: !expr pkgsnip::snip_path("rmd-package-notice.Rmd")
```

### Coding style

```{r}
#| label: coding-style
#| child: !expr pkgsnip::snip_path("coding-style-notice.Rmd")
```
